Visualising Life Satisfaction in Countries across Europe: Individual- and Multi-Level Evidence on Cultural and Pecuniary Factors

### 2019-01-30 LaTex/Paper_fulltext.tex
Added 'Data' part
Correct European Value Survey to Study where present

\usepackage{blindtext}
%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

@@

\section{Introduction and Preliminary remarks}
Anecdotal evidence suggests that people spend a significant share of their lifetime working (for a casual calculation 
see: \citet{thompson_what_2016}). Moreover, people's work environment is changing constantly and especially today's 
discussion about the impact of digitalisation on the labour market requires to investigate how occupational factors shape 
people's life in general. Since work constitutes a considerable part of people’s life, satisfaction with one’s job and the
occupational environment must severely determine overall well-being. Drawing on the above-mentioned diversity of 
occupations, their respective circumstances and adaptation to the ‘digital revolution’, this assumption gains even more 
ground and relevance: \textit{If work changes, life changes.} \\
But which work-related factors contribute to a happy - or unhappy - life? Also, how does life satisfaction of the employed
vary across regions and countries? \\
Using data form the European Values Survey (EVS), we calculated multiple regression models to assess the causality of
work-related factors and well-being on the individual level. Moreover, multi-level analyses with regard to social capital and
macroeconomic as well as developmental indicators were performed to account for variation across regions and countries.

\section{Theory and Literature Review}
Although the causal relation between work and happiness/life satisfaction seems straightforward and intuitively correct,
its academic investigation is far from trivial. On the one hand, this appears in light of definitional questions regarding the 
wo variables of interest. On the other hand, operationalising the constructs appropriately remains subject to discussions
(for subjective well-being see: \cite{kahneman_developments_2006,layard_measuring_2010}). Lastly, the causal nature of job and life
satisfaction presents itself as far more complex than intuitively assumed. \\
Each of these three fields is addressed by a comprehensive literature review to set the tone for the subsequent analysis.
As this analysis draws on specific independent variables on the individual level and several factors on higher aggregate
levels (multi-level analysis), their respective relation to life satisfaction, as assessed in the literature, is discussed as well.

@@

>>>>

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

@@

	\section{Introduction and Preliminary remarks}
	Anecdotal evidence suggests that people spend a significant share of their lifetime working (for a casual calculation 
	see: \citet{thompson_what_2016}). Moreover, people's work environment is changing constantly and especially today's 
	discussion about the impact of digitalisation on the labour market requires to investigate how occupational factors shape 
	people's life in general. Since work constitutes a considerable part of people’s life, satisfaction with one’s job and the
	occupational environment must severely determine overall well-being. Drawing on the above-mentioned diversity of 
	occupations, their respective circumstances and adaptation to the ‘digital revolution’, this assumption gains even more 
	ground and relevance: \textit{If work changes, life changes.} \\
	But which work-related factors contribute to a happy - or unhappy - life? Also, how does life satisfaction of the employed
	vary across regions and countries? \\
	Using data form the European Values Study (EVS) and several other sources, we calculated multiple regression models to assess the causality of
	work-related factors and well-being on the individual level. Moreover, multi-level analyses with regard to social capital and
	macroeconomic as well as developmental indicators were performed to account for variation across regions and countries. 
	%% Könntest du den Fokus ein wenig weg von Work und hin auf multilevel + pecuniary/ non-pecuiary setzen, für so viel Fokus haben wir nicht genug work-relatedness
	\section{Motivational Manifesto}
	In a time of widespread digitalisation for many aspects of modern society, 'datafication' and subsequent analysis of data has become ever more prevalent \citep{baack_datafication_2015, lycett_datafication:_2013}. Transparency of data sourcing, data access and methods employed in the course of this analysis is a chief concern of the 'Open Science' movement \citep{delfanti_open_2010}. With more and more transparency, reproducibility of procedures is expected to increase and thus the quality of insights by replication and and improvements of methods through a 'wisdom of the (educated) crowd'. There have been extensive developments in the form of guidelines and protocols for researchers, universities and scientific journals that are aimed at promoting more transparency in the scientific process \citep{nosek_promoting_2015, miguel_promoting_2014}. 
	At the same time, large shares of the population lack the essential skills to participate in the research process or perceive the barrier of entry in acquiring the necessary skills to do so, as unsurmountably high. The concept of 'Citizen Science' has thus emerged sitting at the edge of both science and education. Citizen science projects enlist non-scientiest members of the public to participate in the research (mainly in data collection), allowing to survey large amounts of data, while educating participants about the research topic \citep{shirk_public_2012}. Originally coming from environmental research this approach has already allowed researcher to survey wide ranges of locations and time periods and thus provides access to high-quality data that could quite impossibly be attained by professional research teams on their own \citep{bonney_citizen_2009}.

	Conceptually, 'Open Science' and 'Citizen Science' are deeply intertwined as 'Citizen Science' needs to be as transparent and easily accessible as possible to be effective on a large scale \citep{nov_dusting_2011} and 'Open Science' needs to offer educational value and low entry barriers if it wants to gain attention and participation of a broader audience \citep{newman_future_2012}. We feel committed to the mission of these movements and have thus designed our project in order to advance it for the social sciences.

	\section{Theory and Literature Review}
	Although the causal relation between work and happiness/life satisfaction seems straightforward and intuitively correct,
	its academic investigation is far from trivial. On the one hand, this appears in light of definitional questions regarding the 
	wo variables of interest. On the other hand, operationalising the constructs appropriately remains subject to discussions
	(for subjective well-being see: \citet{kahneman_developments_2006,layard_measuring_2010}). Lastly, the causal nature of job and life
	satisfaction presents itself as far more complex than intuitively assumed. \\
	Each of these three fields is addressed by a comprehensive literature review to set the tone for the subsequent analysis.
	As this analysis draws on specific independent variables on the individual level and several factors on higher aggregate
	levels (multi-level analysis), their respective relation to life satisfaction, as assessed in the literature, is discussed as well.

@@

	\section{Data}
	All data employed in this project i acquired from official sources and with permission of the provider or in the course of open access. Data as well as original codebooks will be made available for the user upon request, or delivered within the project.
	The project is mainly built on data from the 'European Value Study 2008' (EVS), which is the fourth survey wave \citep{evs_european_2016}. The EVS contains questions regarding values of Europeans on aspects like moral, work, family, politics, society, religion, as well as an extensive collection of sociodemographic items. Issues and questions regarding surveying of the data, errata, harmonizing of results etc. may be settled with the publisher or from the original codebook.
	The file contains a total 66281 observations for 477 variables over 46 European countries. All transformations on variables can be read in detail in the codebook. Significant changes to the data were made through exclusion of 'Russian Federation' from the sample for the purpose of better visualisation. Furthermore, 'Northern Cyprus' and 'Northern Ireland' which were coded as own countries were added to their respective states after international law. Thus, data for 43 countries was processed for use in the project. Furthermore, aggregations were made from the data in total of 5 cases to create variables that are applicable for multilevel analysis. Finally, a variable of 'Geographical region' was created from the country variable in the EVS. This classification was based on the 'Standard Country or Area Codes for Statistics Use' from the UN Statistics Division.
	Structural data for nations was obtained from the World Bank for 'GDP per capita of 2008' (in 2018 dollars per inhabitant), and for 'Gini Coefficient 2008' (in ration scale 0-1). In the case of 'Gini Coefficient 2008', missing values for Germany, Poland, Serbia, Kosovo, Macedonia, Croatia and Bosnia Herzegovina were taken from Eurostat 2008 (Germany, Poland), from the CIA World Factbook (Serbia 2008) from World Bank Gini Coefficient 2009 (Kosovo, Macedonia, Croatia), and from World Bank Gini Coefficient 2007 (Bosnia Herzegovina). Data was also obtained from the 'Democracy Cross-National' dataset created by Pippa Norris for the Freedom House Democracy rating 2008 and the Human Development Index 2008. Missing values of the Freedom House rating for Kosovo and Montenegro were replaced by the indication for 2008 on the Freedom House website. Missing values of the HDI for Kosovo was approximated by the value for Serbia in 2008.

\section{Responsibility for Project Areas}

	\begin{tabular}{|c|c|c|}
		\hline 
		\textbf{Project area}	& \textbf{Noah Peters} 	& \textbf{Nicolas Goeller} 	\\ 
		\hline 
		Data wrangling			&  		   				&  				 			\\ 
		\hline 
		Variable preparation 	&  		   				&  				 			\\ 
		\hline 
		Geodata					&  		   				&  				 			\\ 
		\hline 
		Git	     			 	&  		   				&  				 			\\ 
		\hline 			
		Indices				 	&  		   				&  				 			\\ 
		\hline 
		Paper visualisations 	&  		   				&  				 			\\ 
		\hline 
		Shiny 				 	&  		   				&  				 			\\ 
		\hline 
		Codebook 			 	&  		   				&  				 			\\ 
		\hline 
		Geoplots 			 	&  		   				&  				 			\\ 
		\hline 
		LaTex				 	&  		   				&  				 			\\ 
		\hline 
		Motivation			 	&  		   				&  				 			\\ 
		\hline 
		Theory				 	&  		   				&  				 			\\ 
		\hline 
		User manual			 	&  		   				&  				 			\\ 
		\hline 
	\end{tabular}
